---
title: "Untitled"
author: "Mike Martos"
date: "July 14, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r librariesData}
library(Sleuth3)
ex0727
library(mosaic)


```

###a. A Scatterplot with confidence intervals of the regression line and prediction intervals of the regression line.
```{r 1a}
xyplot(Tcell ~ Mass, panel = panel.lmbands, data = ex0727)
```
###b. A table showing the t-statistics and pvalues for the significance of the regression parameters: ??0 and &beta1.

```{r 1b}
lm1 = lm(Tcell ~ Mass, data = ex0727)
summary(lm1)
```
###Bo : 0.08750
###B1 : 0.03282

###c. Using the data in ii show all 6 steps of each hypothesis test.

###Hypothesis Test Bo
####Step 1: Ho: Bo = 0, Ha: Bo <> 0
####Step 2: alpha: 0.05, df=19, t0.025,19 = +/-2.093
####Step 3: t statistic : 1.112
####Step 4: P-Value : 0.27996
####Step 5: Fail to reject null hypothesis
####Step 6: At a 95% significance level, there is not enough evidence (pValue:0.28) to suggest that Bo is different from Zero.

###Hypothesis Test B1
####Step 1: Ho: Bo = 0, Ha: Bo <> 0
####Step 2: alpha: 0.05, df=19, t0.025,19 = +/-2.093
####Step 3: t statistic : 3.084
####Step 4: P-Value : 0.006
####Step 5: Reject null hypothesis
####Step 6: At a 95% significance level, there is enough evidence with a p-value of 0.006 to suggest that B1 is different to zero.

###d. The regression equation.
#### y = Bo + B1x :  y = 0.0875 + 0.03282x 

###e. Interpretation of the slope and intercept in the model (regression equation.)
#### The Tcell count increases in 0.03 for every gr heavier the mean of the weights of the rock a Black Wheatear carries. Being the intercept very close to 0

###f. Pick a stone mass and find and interpret the 95% confidence interval for the mean t-cell response conditional on that mass.

```{r confidence}
lm3 = lm(Tcell ~ Mass, data = ex0727) 
summary(lm3)
newdata = data.frame(Mass=4)
predict(lm3, newdata, interval="confidence") 
```
###g. For that stone mass, find and interpret the 95% prediction interval for the predicted t-cell response given that mass.
```{r confidence}
lm3 = lm(Tcell ~ Mass, data = ex0727) 
summary(lm3)
predict(lm3, newdata, interval="interpret") 
```
####At a 95% significance level, for a random Black Wheater

```{r pressure, echo=FALSE}


```


h. Using the graphical method, find and interpret the calibration intervals for the t-cell response of 0.3. (Both for mean t-cell response and for a single t-cell response.
i. Find the same calibration intervals analytically using the SE equations given in class and in the book (Version 3 page 194).
j. A scatterplot of residuals.
k. A histogram of residuals with normal distribution superimposed. (from SAS).
